The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-18 paper.tex
Fixed again subsectionning
Moved section on Disruptive behaviours to section on Dynamics of Anthropo
Split the section on Measuring anthropo into the introduction ('few results from the field') and the discussion 'measuring anthropo')

\section*{Introduction and overview}
\label{sec:intro}

@@

@@

\section{Why do people anthropomorphize?}
\label{sec:explanations}

@@

\paragraph{Qualitative assessment of anthropomorphism} The main tools for
qualitative measurement of anthropomorphic effect are questionnaires. We have
explored both Likert-scale and open questions.

Questionnaires are analyzed such as points are 
attributed for key answers, leading to a 
qualitative score:

Fig.~\ref{qualitative-score} plots the qualitative vs quantitative assessment of
anthropomorphic effects during the \emph{Dominos} experiment: the correlation is
negative. The more the children interacted with the robot, the less they
projected anthropomorphic traits on the robot. We also note a remarkable cluster
of seven groups of children who did not interact much with the robot, but had a
strongly anthropomorphic perception of the robot. This may initially look
counter-intuitive (one could hypothesize that the more playful the children are
with the robot, the more likely they are to consider it as a friend/pet/lively
being) and we discuss at section~\ref{sec:cognition-neuroscience} possible
cognitive explanations.

@@

@@

\begin{figure}\footnotesize
    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
     & Unplanned by the robot & Planned by the robot \\ \hline
    Perceived as non-intentional & case I  & case IIIa  \\ \hline
    Perceived as intentional &  case IIIb & case II 
    \end{tabular}
\caption{
    Behaviors of the robot that are unexpected by the user may be intentional
    (the robot has planned the behavior) or not (typically, a failure:
    misdetection, bug,...). Independently of that, the behavior may be
    \emph{perceived} by the user as intentional or not.}
\label{fig:perceptionUnexpectedBehavior}
\end{figure}

@@

This interpretation of anthropomorphism in terms of cognitive correlates opens
questions that we hope could be fruitfully discussed during the workshop.  By
adopting both a cognitive and a dynamic perspective on the anthropomorphic bonds
that establish between a robot and a human during an interaction, some
observations can be raised.

@@

\paragraph*{How to measure anthropomorphism?}

As anthropomorphism emerges from an interaction between a human and a non-human agent, we believe that showing pictures of different kinds of robots and then using questionnaires to measure anthropomorphism is somehow limited. We discuss what tools and measurements could be used to study anthropomorphism and its dynamics in interaction studies in real-world environments.

>>>>

\section{Introduction and overview}
\label{sec:intro}

@@

\subsection{A few results from the field}

Figure~\ref{qualitative-score} plots the qualitative vs quantitative assessment of
anthropomorphic effects during the \emph{Dominos} experiment: the correlation is
negative. The more the children interacted with the robot, the less they
projected anthropomorphic traits on the robot. We also note a remarkable cluster
of seven groups of children who did not interact much with the robot, but had a
strongly anthropomorphic perception of the robot. This may initially look
counter-intuitive (one could hypothesize that the more playful the children are
with the robot, the more likely they are to consider it as a friend/pet/lively
being) and we discuss at section~\ref{sec:cognition-neuroscience} possible
cognitive explanations.

\subsection{Towards an understanding of anthropomorphism}

\fxnote{state here our main research hypothesis}
\fxnote{state here our main contributions}
\fxnote{Introduce the remainder of the paper}

@@

\subsection{Why do people anthropomorphize?}
\label{sec:explanations}

@@

@@

\begin{figure}\footnotesize
    \centering
    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
     & Unplanned by the robot & Planned by the robot \\ \hline
    Perceived as non-intentional & case I  & case IIIa  \\ \hline
    Perceived as intentional &  case IIIb & case II 
    \end{tabular}
\caption{
    Behaviors of the robot that are unexpected by the user may be intentional
    (the robot has planned the behavior) or not (typically, a failure:
    misdetection, bug,...). Independently of that, the behavior may be
    \emph{perceived} by the user as intentional or not.}
\label{fig:perceptionUnexpectedBehavior}
\end{figure}

@@

@@

\subsection{General observations}

By adopting both a cognitive and a dynamic perspective on the anthropomorphic
bonds that establish between a robot and a human during an interaction, some
observations can be raised.

@@

\fxwarning{To be completed/rephrased into a discussion}

\paragraph{Qualitative assessment of anthropomorphism} The main tools for
qualitative measurement of anthropomorphic effect are questionnaires. We have
explored both Likert-scale and open questions. In the Dominos experiment,
questionnaires were analyzed such as points are attributed for key answers,
leading to a qualitative score:
